How to Name a Real-World Object, and how not to

### 2019-12-07 papers/ACL2020/manynames.tex
[ACL2020] more in experiments
on paragraph "Identifying entry-level names requires many annotators"

We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}). 
Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{|ll|ll|}
		\hline
		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
		Images: & 19427 &
			Annotators: & 255 \\
		Img-name pairs: & 69356 &
			Annotators/task: & $\geq$ 3 \\
		Tasks: & 3052 &
			Adeq. mean: & \hspace{-3em}.80 (std .093)\\
		Images/task: & 6-7 &			
			Agreement (adeq.) & 88\% \\ 
		Names/task: & 20-30 &
			Agr. (inadeq. type): & 86\% \\
		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
			Agr. (same-obj): & 94\% \\
		\hline
	\end{tabular}
	\caption{Verification task overview.}
	\label{tab:verification-numbers}
\end{table}
Average name adequacy, encoded on a scale $[0,1]$, is 0.80 with small standard deviation (0.093). 
Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
This level is agreement is high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
\begin{figure}[t]
	\centering
	\hspace*{.2\columnwidth}\includegraphics[width=.7\columnwidth]{images/verification_piechart.pdf}
	\caption{Verification results (counting individual annotations). Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}

@@

\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?} In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.

@@

\paragraph{Entry-level Names are Instance-Dependent:} In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name. The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names). Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \textit{duck} is named \textit{bird} by most annotators. We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g. \textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).
\sz{does this solve this? Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)} \gbt{But, what's an object class in our data? We can't really use collection synsets, can we? Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''. Matthijs is on it.}

\begin{itemize}
	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs. 1 vs. 2 vs. 3). (i.e.,\ entry-level names cannot be derived from a few annotators). \gbt{UPDATE:}
          \begin{itemize}
          \item The average change in most frequent name across rounds is 20\% (SD 2.4\%) -- i.e. even having 9 names only assures you to get the entry-level name for 80\% of the objects on average. \gbt{The data would be more compelling if we did proper sampling (samples of 1, 2, 3, ... names). Matthijs is on it. }
          \end{itemize}

\end{itemize}

@@

@@

We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object. \mw{But this is not as bad as it sounds! It's often quite plausible, e.g., that food names the pizza, not the topping!}
This way, our method may slightly underestimate the number of names per object.
The alternative -- soft clustering, where each name could potentially be in multiple clusters -- would risk overestimating the number of names per object, as well as the number of named objects in an image.

\mw{I realize the foregoing is quite cryptical... Sorry no more time to work on this today!}

>>>>

We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}). 
Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{|ll|ll|}
		\hline
		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
		Images: & 19427 &
			Annotators: & 255 \\
		Img-name pairs: & 69356 &
			Annotators/task: & $\geq$ 3 \\
		Tasks: & 3052 &
			Adeq. mean: & \hspace{-3em}.80 (std .093)\\
		Images/task: & 6-7 &			
			Agreement (adeq.) & 88\% \\ 
		Names/task: & 20-30 &
			Agr. (inadeq. type): & 86\% \\
		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
			Agr. (same-obj): & 94\% \\
		\hline
	\end{tabular}
	\caption{Verification task overview.}
	\label{tab:verification-numbers}
\end{table}
Average name adequacy, encoded on a scale $[0,1]$, is 0.80 with small standard deviation (0.093). 
Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
This level is agreement is high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
\begin{figure}[t]
	\centering
	\hspace*{.2\columnwidth}\includegraphics[width=.7\columnwidth]{images/verification_piechart.pdf}
	\caption{Verification results (counting individual annotations). Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
	\label{fig:verification-piechart}
\end{figure}
\mw{Possibly a pie-chart counting actual names and their aggregated (+thresholded) scores would be more informative than the current pie-chart, which counts original (i.e., non-aggregated) verification annotations.}

We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
For this, we need to compute clusters of names (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships (which could be gotten from, e.g., WordNet) -- rather, we care about (and asked our annotators) which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top.
Moreover, although (hard) clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.

@@

\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?}
\mw{I'd definitely put this in the introduction, and leave only a reminder here.}
In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.
\mw{We could also consider defining entry-level name as `the most frequent adequate name'? Or perhaps as `the most frequent name \emph{if it is adequate}, none otherwise'? Depending on what makes the narrative easier.}

\mw{Also make sure to define the notion of `entry-level object', or `canonical object' perhaps? i.e., the object/cluster of the entry-level name.}

@@

\paragraph{Entry-level Names are Instance-Dependent:} In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name. The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names). Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \textit{duck} is named \textit{bird} by most annotators. We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g. \textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).

\sz{does this solve this? Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)} \gbt{But, what's an object class in our data? We can't really use collection synsets, can we? Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''. Matthijs is on it.}

@@

\paragraph{Identifying entry-level names requires many annotators}
ManyNames was collected in four rounds of 9 annotators each.
On average, the most frequent names differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
\begin{figure}[t]
	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
	\caption{\mw{plot to be improved, rerun on all data, properly framed, captioned, lines becoming horizontal}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the most frequent name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
The blue line shows that, even after gathering 10 names, the entry-level name has been identified with 95\% confidence for only 69\% of objects.
Gathering 20 names increases this to 82\%.
The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
Both lines level level out after gathering 23-25 names, reflecting that for 12\%-15\% of objects even gathering more than 25 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I lack a proper overview to be able to tell.}

%%%%%% BY SAMPLING, FOR GEMMA:
% For each object that has an adequate entry-level name (adequacy $<.5$ according to our Verification results), we randomly sampled (including duplicates) a list of 36 names using the proportions in ManyNames as sampling probabilities, and computed the lowest number of collected names (i.e., the lowest index in the list) after which the entry-level name would reliably remain the most frequent one.
% We did this 30 times for each object.
% The blue line in the figure shows that, after collecting 10 names, the entry-level name is reliably identified for on average around 85\% of objects; collecting 20 names increases this to 90\%.\footnote{
%	But even when gathering 36 names, for around 6\% of objects this can still result in a different entry-level name. This reflects the existence of objects with no clear entry-level name, e.g., where two (almost) equally frequent names are both candidates.
%	\mw{Can we quantify this?}
%}
%The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
%by discarding names for other objects, the entry-level name for the intended object can be identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
%\begin{figure}[t]
%	\includegraphics[width=\columnwidth]{images/stability-all-05-05-spellchecked.png}
%	\caption{}
%	\label{fig:entry-level-name-stability}
%\end{figure}

@@
